Sara Benist MADA Project

### 2023-05-05 products/manuscript/Manuscript.qmd
Final project commit

After processing the data, the `otherburden` and `highburden` datasets were described by exploring each health equity indicators and tuberculosis outcome. The table below shows the list of indicators, and the codebook can be found in the README.md file.

```{r}
#| label: fig-indicators
#| fig-cap: "Healthy equity indicators"
readRDS(file = here("results", "processing", "indicators.rds"))
```

>>>>

After processing the data, the `otherburden` and `highburden` datasets were described by exploring each health equity indicators and tuberculosis outcome. The codebook with indicator descriptions can be found in the README.md file.
